---
title: "Clinic visit scores: group report"
author: "Group N"
format: html
---

```{r}
#| label: setup
#| message: false
source("R/01-clean.R")
source("R/02-describe.R")
source("R/03-model.R")

d <- load_visits()
```

## Data

The data are **simulated** (see `data-raw/00-simulate-data.R`). Nothing here is
an empirical finding; the file exists so that this project has something to
analyse while we learn git.

`r nrow(d)` simulated participants, `r nlevels(d$arm)` arms.

## Descriptives

<!-- student B writes here -->

```{r}
#| label: describe
knitr::kable(describe_visits(d))
```

Split by sex as well, since the arms were balanced by design but sex was not:

```{r}
#| label: describe-by-sex
knitr::kable(describe_by_sex(d))
```

## Model

<!-- student C writes here -->

```{r}
#| label: model
fit <- model_visits(d)
knitr::kable(model_table(fit))
```

## Interpretation

<!-- EVERYONE edits this section. This is where merge conflicts happen. -->

In this simulated dataset the treatment arm scored about 5 points lower
than control after adjustment for age and sex. Because the data were
generated with a known arm effect of -4, the estimate is close to the
truth but not identical - ordinary sampling variation.
